### 2020-05-18 README.Rmd
fix another typo
fix typo: Wabha -> Wahba

```{r appraise-figure, dev = "png", fig.height = 6, fig.width = 9, dpi = 120, echo = FALSE, fig.show = "hide", dependson = -1}
appraise(m)
```

@@

    For example, the classic four term additive example from Gu & Wabha:

>>>>

```{r appraise-figure, dev = "png", fig.height = 6, fig.width = 9, dpi = 120, echo = FALSE, fig.show = "hide", dependson = -1}
appraise(m1)
```

@@

    For example, the classic four term additive example from Gu & Wahba:
